\Large\bf FlexibleSUSY 2.0: Extensions to investigate the phenomenology of SUSY and non-SUSY models

### 2018-02-22 doc/flexiblesusy-2.0.tex
update FS-2.0 paper (version re-submitted to CPC, commit 1d558aec475d)

@@

  \begin{abstract}
    We document major new features and improvements
    of \fs, a \mathematica and
    C++ package that generates fast and precise spectrum
    generators. These extensions significantly increase the generality
    and capabilities of the \fs package, while maintaining the elegant
    structure and easy to use interfaces. The \fbsm extension makes it
    possible to also create spectrum generators for non-supersymmetric
    extensions of the Standard Model. The \fcpv extension adds the
    option of complex parameters to the spectrum generators, allowing
    the study of many interesting models with new sources of \CP
    violation. \fmw computes the decay of the muon for the generated
    model and thereby allows \fs to predict the mass of the $W$ boson
    from the input parameters by using the more precise electroweak
    input of $\{ G_F, M_Z, \aem \}$ instead of $\{ M_W, M_Z,
    \aem \}$. The \famu extension provides a calculator of the
    anomalous magnetic moment of the muon in any model \fs can
    generate a spectrum for.  \fsas introduces a new solver for the
    boundary value problem which makes use of semi-analytic expressions
    for dimensionful parameters to find solutions in models
    where the classic two-scale solver will not work such as the constrained
    E$_6$SSM\@. \feft is a hybrid calculation of the Higgs mass which
    combines the virtues of both effective field theory calculations
    and fixed-order calculations.  All of these extensions are
    included in \fstwo, which is released simultaneously with this
    manual.
  \end{abstract}

@@

Popular and well studied new physics extensions of the Standard Model
(SM) are coming under increasing pressure from the searches
at the Large Hadron Collider (LHC) as well as other current experiments.
At the same time, there remain many outstanding physics problems that are not
solved by the SM and require new physics.  For example, the origin of dark
matter is still unexplained and it requires some new particle
to fit the relic density.  In addition, the gauge structure and
fractional charges of the SM have no explanation, but some
observations hint at the possibility of a grand unified theory (GUT)
from which these can be derived after the breakdown of the GUT gauge
group.  Finally, the stability of the weak scale, which is $17$ orders
of magnitude smaller than the Planck scale, has no explanation within
the SM and has been the driving motivation for the construction and study
of concepts that go beyond the Standard Model (BSM), most notably supersymmetry
(SUSY) \cite{Weinberg:1975gm, Weinberg:1979bn, Gildener:1976ai,Susskind:1978ms,
  tHooft:1980xss}.

@@

\fs \cite{Athron:2014yba,Athron:2016fuq} already made a significant
push in this direction, allowing the automatic creation of a spectrum
generator for a very wide range of supersymmetric models.  \fs uses
\sarah \cite{Staub:2010ty,Staub:2009bi,Staub:2010jh,Staub:2012pb,
  Staub:2013tta} to obtain \mathematica expressions for model dependent
components, the 2-loop renormalization group equations (RGEs),
1-loop self energies, 1-loop tadpoles, mass matrices and
electroweak symmetry breaking (EWSB) conditions. \fs then translates these
expressions into C++ routines and embeds them inside a code structure
for solving the boundary value problem (BVP)\@.  It also uses some numerical
routines from \softsusy \cite{Allanach:2001kg,Allanach:2013kza} and is
heavily unit-tested against the MSSM and Next-to-MSSM versions of
\softsusy every night to avoid bugs.

@@

\subsection{Downloading \fs and generating a first spectrum generator}
\label{sec:quick-start-cmssm}
\fs is available as gzipped tarball on
[\url{http://flexiblesusy.hepforge.org}] or
[\url{https://github.com/FlexibleSUSY/FlexibleSUSY}] under the version
control system \texttt{git}.
%
To download and install \fstwo as a gzipped tarball run at the command
line:
%
\begin{lstlisting}[language=bash]
$ wget https://www.hepforge.org/archive/flexiblesusy/FlexibleSUSY-2.0.1.tar.gz
$ tar -xf FlexibleSUSY-2.0.1.tar.gz
$ cd FlexibleSUSY-2.0.1
\end{lstlisting}%% $
%
\fstwo is distributed with a huge selection of predefined models
including: the CMSSM (called \modelname{CMSSM}), the semi-constrained and
fully constrained NMSSM (\modelname{NMSSM}, \modelname{CNMSSM}), the
$R$-symmetric MSSM (\modelname{MRSSM}) \cite{Kribs:2007ac}, the NUHM \ESSM
(\modelname{E6SSM}) \cite{Athron:2007en}, high-scale SUSY (\HSSUSY)
\cite{Bagnaschi:2015pwa}, split-SUSY (\modelname{SplitMSSM})
\cite{Bagnaschi:2015pwa} and the THDM-II (\modelname{THDMII}).  See the
contents of \code{model_files/} for all predefined model files.

A spectrum generator for any of these models can be built with just
three commands.  For example, the CMSSM spectrum generator can be
created by running the following shell commands:
%
\begin{lstlisting}[language=bash]
$ ./createmodel --name=CMSSM
$ ./configure --with-models=CMSSM
$ make
\end{lstlisting}%% $
%
The \code{createmodel} command creates the model directory
\code{models/CMSSM/} where the code will be generated and adds the
CMSSM model file and an example SLHA input file to it.  The \code{configure}
script sets up the \code{Makefile}, checking the system requirements
and dependencies.  For more options see \code{./configure
  --help}.  The last command creates the code for the spectrum
generator of this model and compiles it.
%
This generated spectrum generator can then be run from the command
line as:
%
\begin{lstlisting}[language=bash]
$ cd models/CMSSM
$ ./run_CMSSM.x --slha-input-file=LesHouches.in.CMSSM \
                --slha-output-file=LesHouches.out.CMSSM
\end{lstlisting}
%
The spectrum generator reads the CMSSM input parameters from the SLHA input file
\code{LesHouches.in.CMSSM} and first solves a BVP to find a
set of running parameters at the \code{SUSYScale} that are consistent with all
boundary conditions specified in the model file, and then calculates the pole
masses, mixing matrices and potentially further observables.
The mass spectrum etc.\ obtained in this way is output
in SLHA format \cite{Skands:2003cj,Allanach:2008qq} as
\code{LesHouches.out.CMSSM}.  See \code{./run_CMSSM.x --help} for more
options.

@@

\begin{OptionTable}{\fs model file switches to enable/disable
    model-specific higher-order contributions in the SM,
    MSSM, NMSSM and split-MSSM.}{tab:fbsm_options}[lllX]
  %
  \multicolumn{4}{c}{\textit{SM}}\\
  \midrule
  \code{UseHiggs2LoopSM} & \code{False} & \code{True} or \code{False}
  & 2-loop contributions $O(\at^2 + \at \as)$ to $M_h$ in the SM \\
  %
  \code{UseHiggs3LoopSM} & \code{False} & \code{True} or \code{False} &
  3-loop contributions $O(\at^3 + \at^2 \as \allowbreak + \at \as^2)$ to $M_h$ in
  the SM \\
  %
  \code{UseSM3LoopRGEs} & \code{False} & \code{True} or \code{False} &
  3-loop RGEs in the SM \\
  %
  \code{UseYukawa3LoopQCD} & \code{Automatic} & \multilinecell[t]{\code{True} or \code{False}\\ or \code{Automatic}} &
  2-loop and 3-loop QCD contributions $O(\as^2 + \as^3)$ to the \MSbar $y_t$ in the SM \\
  %
  \code{UseSMAlphaS3Loop} & \code{False} & \code{True} or \code{False}
  & 2-loop and 3-loop QCD threshold corrections
  $O(\as^2 + \as^3)$
  to the \MSbar $\as$ in the SM \\
  %
  \midrule
  \multicolumn{4}{c}{\textit{MSSM}}\\
  \midrule
  %
  \code{UseHiggs2LoopMSSM} & \code{False} & \code{True} or \code{False} &
  2-loop contributions $O((\at + \ab)\as \allowbreak + (\at +
  \ab)^2 \allowbreak + \atau^2)$ to $M_h$, $M_H$ and $M_A$ in
  the MSSM \\
  %
  \code{UseHiggs3LoopMSSM} & \code{False} & \code{True} or
  \code{False} & 3-loop contributions
  $O(\at\as^2 \allowbreak + \ab\as^2)$ to $M_h$ in
  the MSSM (requires \Himalaya) \\
  %
  \code{UseMSSM3LoopRGEs} & \code{False} & \code{True} or \code{False} &
  3-loop RGEs in the MSSM \\
  %
  \code{UseMSSMYukawa2Loop} & \code{False} & \code{True} or \code{False} &
  2-loop \SQCD contribution $O(\as^2)$ to the \DRbar $y_b$ and $y_t$ in the MSSM \\
  %
  \code{UseMSSMAlphaS2Loop} & \code{False} & \code{True} or
  \code{False} & 2-loop \SQCD contribution
  $O(\as^2 + \as\at + \as\ab)$
  to the \DRbar $\as$ in the MSSM \\
  %
  \midrule
  \multicolumn{4}{c}{\textit{NMSSM}}\\
  \midrule
  %
  \code{UseHiggs2LoopNMSSM} & \code{False} & \code{True} or \code{False} &
  2-loop contributions $O((\at + \ab)\as \allowbreak + (\at +
  \ab)^2 \allowbreak + \atau^2)$ to $M_{h_i}$ and $M_{A_i}$ in
  the NMSSM \\
  %
  \midrule
  \multicolumn{4}{c}{\textit{split-MSSM}}\\
  \midrule
  %
  \code{UseHiggs3LoopSplit} & \code{False} & \code{True} or \code{False} &
  3-loop contributions $O(\at\as^2)$ to $M_h$, $M_H$ and
  $M_A$ in the split-MSSM \\
  %
  \bottomrule
\end{OptionTable}

@@

In the SM, 2-loop and leading 3-loop contributions to the Higgs pole
mass are known in the \MSbar scheme
\cite{Degrassi:2012ry,Martin:2014cxa,Vega:2015fna}.  In \fs the 2-loop
contributions of $O(\at^2 + \at \as)$
\cite{Degrassi:2012ry,Martin:2014cxa} and the 3-loop
$O(\at^3 + \at^2 \as + \at \as^2)$ contributions \cite{Martin:2014cxa}
can be taken into account to calculate the SM-like Higgs pole mass for
non-SUSY models with only one Higgs.  In order to enable these loop
contributions, the following switches must be set in the model file:
%
\begin{lstlisting}
UseHiggs2LoopSM = True;
UseHiggs3LoopSM = True;
\end{lstlisting}
%
The enabled 2-loop SM contributions of
$O(\at^2 + \at \as)$ to the Higgs mass read
%
\begin{align}
  (\Delta m_h^2)_{2L} &= (\Delta m_h^2)_{2L}^{(\at^2)} + (\Delta m_h^2)_{2L}^{(\at\as)} \,, \\
  (\Delta m_h^2)_{2L}^{(\at^2)} &=
  \frac{2 t}{(4\pi)^4} \left[
    -3 y_t^4 \left(3 \;\barlog^2(t) - 7 \;\barlog(t) + 2 + \frac{\pi^2}{3}\right)
  \right] , \label{eq:2L_Mh_atat}\\
  (\Delta m_h^2)_{2L}^{(\at\as)} &=
      \frac{g_3^2 y_t^2}{(4\pi)^4} \;\bigg[
        \frac{37}{3} p^2 - \frac{122 p^4}{135 t} - 4 (5 p^2 - 8 t) \;\barlog(t) -
        12 (p^2 - 8 t) \;\barlog^2(t) \bigg] \label{eq:2L_Mh_atas} \\
  &\stackrel{\mathmakebox[\widthof{=}]{p^2=0}}{=} \
  \frac{2 t}{(4\pi)^4} \left[
    16 g_3^2 y_t^2 \left(3 \;\barlog^2(t) + \barlog(t)\right)
  \right] \,.
\end{align}
%
In Eqs.~\eqref{eq:2L_Mh_atat} ff.\ the abbreviations
$t \equiv m_t^2$ and $\barlog(t) \equiv \log(t/Q^2)$ have been used
for brevity, analogous to the notation of Ref.~\cite{Martin:2014cxa},
where $m_t$ is the \MSbar top mass in the SM\@.  Note
that the momentum dependence is included in the 2-loop expression of
Eq.~\eqref{eq:2L_Mh_atas} in order to generate implicit 3-loop
$O(\at^2\as)$ terms.
%
The explicit 3-loop effective potential contributions of
$O(\at^3 + \at^2 \as + \at \as^2)$ to the
Higgs mass included by \fs read
%
\begin{align}
  (\Delta m_h^2)_{3L} &=
  \frac{m_t^2}{(4\pi)^6} \Bigg[
     g_3^4 y_t^2 \left(248.122 + 839.197 \;\barlog(t) + 160 \;\barlog^2(t) - 736 \;\barlog^3(t)\right) \nonumber \\
     &\phantom{=\frac{m_t^2}{(4\pi)^6} \Bigg[}
     + g_3^2 y_t^4 \left(2764.365 + 1283.716 \;\barlog(t) - 360 \;\barlog^2(t) + 240 \;\barlog^3(t)\right) \nonumber \\
     &\phantom{=\frac{m_t^2}{(4\pi)^6} \Bigg[}
     + y_t^6 \Big(-3199.017 + 36 \;\barlog(h) - 2653.511 \;\barlog(t) + 756 \;\barlog(h) \;\barlog(t) \nonumber \\
     &\phantom{=\frac{m_t^2}{(4\pi)^6} \Bigg[}\qquad~~
     + \frac{27}{2} \;\barlog^2(t) + 324 \;\barlog(h) \;\barlog^2(t) - 225 \;\barlog^3(t)\Big)
  \Bigg]
\end{align}
%
where $h\equiv m_h^2$ is the squared \MSbar Higgs mass in the SM\@.
Note that the 3-loop Higgs mass calculation in
the \MSbar scheme in \fsbreak is only complete at $O(\at\as^2)$.  The
3-loop contributions of $O(\at^3 + \at^2 \as)$ are currently incomplete
because they would require the \MSbar top Yukawa coupling to be determined
from the top pole mass at the 2-loop $O(\at^2 + \at\as)$.
However, these 2-loop contributions to the top Yukawa coupling are
currently not available in \fs. Furthermore, the proper inclusion of
corrections to the Higgs pole mass at $O(\at^3)$
would require the extension of Eq.~\eqref{eq:2L_Mh_atat} by momentum
dependent $O(\at^2)$ terms. Alternatively, the evaluation of the Higgs mass at
the renormalization scale $Q^2 = t$ implies that the neglected
3-loop contributions at $O(\at^3 t)$ vanish
\cite{Martin:2014cxa}.\footnote{Note that terms of $O(\at^3 h)$ are
  neglected here and in Ref.\ \cite{Martin:2014cxa}.}
Likewise, Eq.~\eqref{eq:2L_Mh_atat} neglects contributions of $O(\at^2h)$ which are
subdominant in comparison to the implemented $O(\at^2t)$ corrections.
In contrast, the QCD corrections to the pole mass at 2-loop level, Eq.~\eqref{eq:2L_Mh_atas}, involve
terms proportional to the quartic Higgs coupling $\lambda$ up to $O(\as\at h^2/t)$, which are not
neglected here.

@@

In the right panels of \figref{fig:Mh-himalaya}, the effect of the 2-loop
\SQCD threshold correction $\Delta\as^{2L}$
\cite{Harlander:2005wm,Bauer:2008bj,Bednyakov:2010ni} to the strong
coupling $\as$ (see below) on the 3-loop Higgs mass calculation is shown for
the same scenario as in the corresponding left panels.  The inclusion
of $\Delta\as^{2L}$ is formally a 4-loop effect on the light
\CP-even Higgs mass in the MSSM\@.  However, $\Delta\as^{2L}$ should
be taken into account for a consistent running and decoupling
procedure with 3-loop renormalization group running.  The red solid
lines in the right panels correspond to the 3-loop calculation of
Ref.~\cite{Harlander:2017kuc}, which uses only the 1-loop threshold correction
$\Delta\as^{1L}$.  These red solid lines are the same as in the
corresponding left panels.  The effect of including
$\Delta\as^{2L}$ is shown as the red dashed line.  We find that the
inclusion of this 2-loop threshold correction leads to an upwards
shift of the Higgs mass by up to $2\unit{GeV}$, depending on \MS and
$X_t$.

@@

@@

The \fs user interface for creating spectrum generators for non-SUSY
models is exactly the same as in the case of SUSY models, except that
all non-SUSY parameters are defined in the \MSbar scheme.  In
particular, at the low-energy scale \fs automatically determines
the gauge and Yukawa couplings of the non-SUSY model in the \MSbar
scheme.

@@

>>>>

\newcommand{\MLCP}{\ensuremath{M_\text{LCP}}\xspace}

@@

  \begin{abstract}
    We document major new features and improvements of \fs, a
    \mathematica and C++ package with a dependency on the external
    package \sarah, that generates fast and precise spectrum
    generators. The extensions presented here significantly increase
    the generality and capabilities of the \fs package, which already
    works with a wide class of models, while
    maintaining an elegant structure and easy to use interfaces. The
    \fbsm extension makes it possible to also create spectrum
    generators for non-supersymmetric extensions of the Standard
    Model. The \fcpv extension adds the option of complex parameters
    to the spectrum generators, allowing the study of many interesting
    models with new sources of \CP violation. \fmw computes the decay
    of the muon for the generated model and thereby allows \fs to
    predict the mass of the $W$ boson from the input parameters by
    using the more precise electroweak input of $\{ G_F, M_Z, \aem \}$
    instead of $\{ M_W, M_Z, \aem \}$. The \famu extension provides a
    calculator of the anomalous magnetic moment of the muon in any
    model \fs can generate a spectrum for.  \fsas introduces a new
    solver for the boundary value problem which makes use of
    semi-analytic expressions for dimensionful parameters to find
    solutions in models where the classic two-scale solver will not
    work such as the constrained E$_6$SSM\@. \feft is a hybrid
    calculation of the Higgs mass which combines the virtues of both
    effective field theory calculations and fixed-order calculations.
    All of these extensions are included in \fstwo, which is released
    simultaneously with this manual.%% \sarah, an external dependency
    %% providing model dependent information, can be automaically
    %% installed using an installation script distributed with \fs.
  \end{abstract}

@@

Popular and well studied new physics extensions of the Standard Model
(SM) are coming under increasing pressure from the searches at the
Large Hadron Collider (LHC) as well as other current experiments.  At
the same time, there remain many outstanding physics problems that are
not solved by the SM and require new physics.  For example, the origin
of dark matter is still unexplained and it requires some new particle
to fit the relic density.  In addition, the gauge structure and
fractional charges of the SM have no explanation, but some
observations hint at the possibility of a grand unified theory (GUT)
from which these can be derived after the breakdown of the GUT gauge
group.  Finally, the stability of the weak scale, which is $17$ orders
of magnitude smaller than the Planck scale, has no explanation within
the SM \cite{Weinberg:1975gm, Weinberg:1979bn,
  Gildener:1976ai,Susskind:1978ms, tHooft:1980xss} and has been the
driving motivation for the construction and study of concepts that go
beyond the Standard Model (BSM), most notably supersymmetry (SUSY) \cite{Miyazawa:1966mfa,Miyazawa:1968zz,Ramond:1971gb,Golfand:1971iw,Gervais:1971ji,Neveu:1971rx,Neveu:1971iv,Volkov:1973ix,Wess:1973kz,Wess:1974tw,Salam:1974yz} which ensures that the quadratic corrections from fermions and bosons in the loop diagrams cancel at all orders in perturbation theory \cite{Dimopoulos:1981au,Witten:1981nf,Dine:1981za,Dimopoulos:1981zb,Kaul:1981hi}.

@@

\fs \cite{Athron:2014yba,Athron:2016fuq} already made a significant
push in this direction, allowing the automatic creation of a spectrum
generator for a very wide range of supersymmetric models.  \fs uses
\sarah \cite{Staub:2010ty,Staub:2009bi,Staub:2010jh,Staub:2012pb,
  Staub:2013tta} to obtain \mathematica expressions for model dependent
components, the 2-loop renormalization group equations (RGEs),
1-loop self energies, 1-loop tadpoles, mass matrices and
electroweak symmetry breaking (EWSB) conditions. \fs then translates these
expressions into C++ routines and embeds them inside a code structure
for solving the boundary value problem (BVP)\@.  It also uses some numerical
routines from \softsusy \cite{Allanach:2001kg,Allanach:2013kza} and is
heavily unit-tested against the MSSM and Next-to-MSSM versions of
\softsusy every night to ensure bugs are avoided in updates.

@@

\subsection{Downloading \fs and generating a first spectrum generator}
\label{sec:quick-start-cmssm}
\fs is available as gzipped tarball on
[\url{http://flexiblesusy.hepforge.org}] or
[\url{https://github.com/FlexibleSUSY/FlexibleSUSY}] under the version
control system \texttt{git}.
%
To download and install \fstwo as a gzipped tarball run at the command
line:
%
\begin{lstlisting}[language=bash]
$ wget https://www.hepforge.org/archive/flexiblesusy/FlexibleSUSY-2.0.1.tar.gz
$ tar -xf FlexibleSUSY-2.0.1.tar.gz
$ cd FlexibleSUSY-2.0.1
\end{lstlisting}%% $
%
\fstwo is distributed with a huge selection of predefined ``models'', 
including several MSSM and NMSSM scenarios such as the CMSSM (called
\modelname{CMSSM}), high-scale SUSY and split-SUSY (called \HSSUSY and
\modelname{SplitMSSM}; these  models have been created for
Ref.~\cite{Bagnaschi:2015pwa}), the semi-constrained and
fully constrained NMSSM (\modelname{NMSSM}, \modelname{CNMSSM}). The
distribution also contains BSM models such as the
$R$-symmetric MSSM (\modelname{MRSSM}; for a definition of the model
see Ref.~\cite{Kribs:2007ac}), the NUHM \ESSM
(\modelname{E6SSM}, see \cite{King:2005jy,King:2005my,Athron:2010zz,
  Athron:2009ue,Athron:2009bs,Athron:2007en}) and the two-Higgs 
doublet model type II
(\modelname{THDMII}).  See the 
contents of \code{model_files/} for all predefined model files.

A spectrum generator for any of these models can be built with just
three commands.  For example, the CMSSM spectrum generator can be
created by running the following shell commands:
%
\begin{lstlisting}[language=bash]
$ ./createmodel --name=CMSSM
$ ./configure --with-models=CMSSM
$ make
\end{lstlisting}%% $
%
The \code{createmodel} command creates the model directory
\code{models/CMSSM/} where the code will be generated and adds the
CMSSM model file and an example SLHA input file to it.  The \code{configure}
script sets up the \code{Makefile}, checking the system requirements
and dependencies.  For more options see \code{./configure
  --help}.  The last command creates the code for the spectrum
generator of this model and compiles it.
%
This generated spectrum generator can then be run from the command
line as:
%
\begin{lstlisting}[language=bash]
$ cd models/CMSSM
$ ./run_CMSSM.x --slha-input-file=LesHouches.in.CMSSM \
                --slha-output-file=LesHouches.out.CMSSM
\end{lstlisting}
%
The spectrum generator reads the CMSSM input parameters from the SLHA input file
\code{LesHouches.in.CMSSM} and first solves a BVP to find a
set of running parameters at the SUSY scale that are consistent with all
boundary conditions specified in the model file, and then calculates the pole
masses, mixing matrices and potentially further observables.
The mass spectrum etc.\ obtained in this way is output
in SLHA format \cite{Skands:2003cj,Allanach:2008qq} as
\code{LesHouches.out.CMSSM}.  See \code{./run_CMSSM.x --help} for more
options.

@@

\begin{OptionTable}{\fs model file switches to enable/disable
    model-specific higher-order contributions in the SM,
    MSSM, NMSSM and split-MSSM.}{tab:fbsm_options}[lllX]
  %
  \multicolumn{4}{c}{\textit{SM}}\\
  \midrule
  \code{UseHiggs2LoopSM} & \code{False} & \code{True} or \code{False}
  & 2-loop contributions $O(\at^2 + \at \as)$ to $M_h$ in the SM \\
  %
  \code{UseHiggs3LoopSM} & \code{False} & \code{True} or \code{False} &
  3-loop contributions $O(\at^3 + \at^2 \as \allowbreak + \at \as^2)$ to $M_h$ in
  the SM \\
  %
  \code{UseSM3LoopRGEs} & \code{False} & \code{True} or \code{False} &
  3-loop RGEs in the SM \\
  %
  \code{UseYukawa3LoopQCD} & \code{Automatic} & \multilinecell[t]{\code{True} or \code{False}\\ or \code{Automatic}} &
  2-loop and 3-loop QCD contributions $O(\as^2 + \as^3)$ to the \MSbar $y_t$ in the SM \\
  %
  \code{UseSMAlphaS3Loop} & \code{False} & \code{True} or \code{False}
  & 2-loop and 3-loop QCD threshold corrections
  $O(\as^2 + \as^3)$
  to the \MSbar $\as$ in the SM \\
  %
  \midrule
  \multicolumn{4}{c}{\textit{MSSM}}\\
  \midrule
  %
  \code{UseHiggs2LoopMSSM} & \code{False} & \code{True} or \code{False} &
  2-loop contributions $O((\at + \ab)\as \allowbreak + (\at +
  \ab)^2 \allowbreak + \atau^2)$ to $M_h$, $M_H$ and $M_A$ in
  the MSSM \\
  %
  \code{UseHiggs3LoopMSSM} & \code{False} & \code{True} or
  \code{False} & 3-loop contributions
  $O(\at\as^2 \allowbreak + \ab\as^2)$ to $M_h$ in
  the MSSM (requires \Himalaya) \\
  %
  \code{UseMSSM3LoopRGEs} & \code{False} & \code{True} or \code{False} &
  3-loop RGEs in the MSSM \\
  %
  \code{UseMSSMYukawa2Loop} & \code{False} & \code{True} or \code{False} &
  2-loop \SQCD contribution $O(\as^2)$ to the \DRbar $y_b$ and $y_t$ in the MSSM \\
  %
  \code{UseMSSMAlphaS2Loop} & \code{False} & \code{True} or
  \code{False} & 2-loop \SQCD contribution
  $O(\as^2 + \as\at + \as\ab)$
  to the \DRbar $\as$ in the MSSM \\
  %
  \midrule
  \multicolumn{4}{c}{\textit{NMSSM}}\\
  \midrule
  %
  \code{UseHiggs2LoopNMSSM} & \code{False} & \code{True} or \code{False} &
  2-loop contributions $O((\at + \ab)\as \allowbreak + (\at +
  \ab)^2 \allowbreak + \atau^2)$ to $M_{h_i}$ and $M_{A_i}$ in
  the NMSSM \\
  %
  \midrule
  \multicolumn{4}{c}{\textit{split-MSSM}}\\
  \midrule
  %
  \code{UseHiggs3LoopSplit} & \code{False} & \code{True} or \code{False} &
  3-loop contributions $O(\at\as^2)$ to $M_h$ in the split-MSSM \\
  %
  \bottomrule
\end{OptionTable}

@@

In the SM, 2-loop and leading 3-loop contributions to the Higgs pole
mass are known in the \MSbar scheme
\cite{Degrassi:2012ry,Vega:2015fna,Martin:2014cxa}.  In \fs the 2-loop
contributions of $O(\at^2 + \at \as)$
\cite{Vega:2015fna,Martin:2014cxa} and the 3-loop
$O(\at^3 + \at^2 \as + \at \as^2)$ contributions \cite{Martin:2014cxa}
can be taken into account to calculate the SM-like Higgs pole mass for
non-SUSY models with only one Higgs. In order to enable these loop
contributions, the following switches must be set in the model file:
UseHiggs2LoopSM = True;
UseHiggs3LoopSM = True;
The 2-loop and 3-loop
contributions enter the mass of the Higgs boson as
\begin{align} 
 \begin{split}
   M_h^2 &= m_h^2 + (\Delta m_h^2)_{1L}(p^2)
   + (\Delta m_h^2)_{2L}(p^2) +(\Delta m_h^2)_{3L} \,,
 \end{split} \label{eq:Mh_polp^2}
\end{align}
where $m_h^2$ and $(\Delta m_h)_{1L}(p^2)$ correspond to the tree-level 
and a 1-loop expression, respectively.
The enabled 2-loop SM contributions of
$O(\at^2 + \at \as)$ to the Higgs mass read
\begin{align}
  (\Delta m_h^2)_{2L}(p^2) &= (\Delta m_h^2)_{2L}^{(\at^2)} + 
     (\Delta m_h^2)_{2L}^{(\at\as)}(p^2) \,, \\
  (\Delta m_h^2)_{2L}^{(\at^2)} &=
  \frac{2 t}{(4\pi)^4} \left[
    -3 y_t^4 \left(3 \;\barlog^2(t) - 7 \;\barlog(t) + 2 + \frac{\pi^2}{3}\right)
  \right] , \label{eq:2L_Mh_atat}\\
  (\Delta m_h^2)_{2L}^{(\at\as)} (p^2)&=
      \frac{g_3^2 y_t^2}{(4\pi)^4} \;\bigg[
        \frac{37}{3} p^2 - \frac{122 p^4}{135 t} - 4 (5 p^2 - 8 t) \;\barlog(t) -
        12 (p^2 - 8 t) \;\barlog^2(t) \bigg] \label{eq:2L_Mh_atas} \\
  &\stackrel{\mathmakebox[\widthof{=}]{p^2=0}}{=} \
  \frac{2 t}{(4\pi)^4} \left[
    16 g_3^2 y_t^2 \left(3 \;\barlog^2(t) + \barlog(t)\right)
  \right] \,.
  \label{eq:2L_Mh_atas p2=0}
\end{align}
In Eqs.~\eqref{eq:2L_Mh_atat} ff.\ the abbreviations $t \equiv m_t^2$
and $\barlog(t) \equiv \log(t/Q^2)$ have been used for brevity, 
analogous to the notation of Ref.~\cite{Martin:2014cxa}, where $m_t$ 
is the \MSbar top mass in the SM\@. 
By performing a momentum iteration in the computation of the Higgs 
pole mass, the momentum entering the 1-loop self energy in 
Eq.~\eqref{eq:Mh_polp^2} consists of a tree-level part and a loop 
correction.
In combination with Eq.~\eqref{eq:2L_Mh_atat}, the latter yields the 
complete Higgs mass contribution at $O(\at^2 t)$ which is identical 
to the corresponding correction given in Ref.~\cite{Degrassi:2012ry}.
The 2-loop self energy at $O(\at\as)$ \cite{Martin:2014cxa} together
with the occurring integral functions from Ref.~\cite{Martin:2003qz}
have been evaluated for a small external momentum argument. Neglecting
higher orders, the expansion in powers of the momentum over the \MSbar
top mass up to $O(p^4/t)$ results in the Eq.~\eqref{eq:2L_Mh_atas}. 
Note that the momentum dependence is included in the 2-loop expression 
in order to generate implicit 3-loop $O(\at^2\as)$ terms.
The explicit 3-loop effective potential contributions of
$O(\at^3 + \at^2 \as + \at \as^2)$ to the
Higgs mass included by \fs read
\begin{align}
  (\Delta m_h^2)_{3L} &=
  \frac{m_t^2}{(4\pi)^6} \Bigg[
     g_3^4 y_t^2 \left(248.122 + 839.197 \;\barlog(t) + 160 \;\barlog^2(t) - 736 \;\barlog^3(t)\right) \nonumber \\
     &\phantom{=\frac{m_t^2}{(4\pi)^6} \Bigg[}
     + g_3^2 y_t^4 \left(2764.365 + 1283.716 \;\barlog(t) - 360 \;\barlog^2(t) + 240 \;\barlog^3(t)\right) \nonumber \\
     &\phantom{=\frac{m_t^2}{(4\pi)^6} \Bigg[}
     + y_t^6 \Big(-3199.017 + 36 \;\barlog(h) - 2653.511 \;\barlog(t) + 756 \;\barlog(h) \;\barlog(t) \nonumber \\
     &\phantom{=\frac{m_t^2}{(4\pi)^6} \Bigg[}\qquad~~
     + \frac{27}{2} \;\barlog^2(t) + 324 \;\barlog(h) \;\barlog^2(t) - 225 \;\barlog^3(t)\Big)
  \Bigg] \,,
\end{align}
where $h\equiv m_h^2$ is the squared \MSbar Higgs mass in the SM\@.
Note that the 3-loop Higgs mass calculation in
the \MSbar scheme in \fsbreak is only complete at $O(\at\as^2)$.  The
3-loop contributions of $O(\at^3 + \at^2 \as)$ are currently incomplete
because they would require the \MSbar top Yukawa coupling to be determined
from the top pole mass at the 2-loop $O(\at^2 + \at\as)$.
However, these 2-loop contributions to the top Yukawa coupling are
currently not available in \fs. Furthermore, the proper inclusion of
corrections to the Higgs pole mass at $O(\at^3)$
would require the extension of Eq.~\eqref{eq:2L_Mh_atat} by momentum
dependent $O(\at^2)$ terms. Alternatively, the evaluation of the Higgs mass at
the renormalization scale $Q^2 = t$ implies that the neglected
3-loop contributions at $O(\at^3 t)$ vanish
\cite{Martin:2014cxa}.\footnote{Note that terms of $O(\at^3 h)$ are
  neglected here and in Ref.\ \cite{Martin:2014cxa}.}
Likewise, Eq.~\eqref{eq:2L_Mh_atat} neglects contributions of $O(\at^2h)$ which are
subdominant in comparison to the implemented $O(\at^2t)$ corrections.
In contrast, the QCD corrections to the pole mass at 2-loop level, Eq.~\eqref{eq:2L_Mh_atas}, involve
terms proportional to the quartic Higgs coupling $\lambda$ up to $O(\as\at h^2/t)$, which are not
neglected here.

@@

In the right panels of \figref{fig:Mh-himalaya}, the effect of the 2-loop
\SQCD threshold correction $\Delta\as^{2L}$
\cite{Harlander:2005wm,Bauer:2008bj,Bednyakov:2010ni} to the strong
coupling $\as$ (see below) on the 3-loop Higgs mass calculation is shown for
the same scenario as in the corresponding left panels.
The threshold correction $\Delta\as^{2L}$ is included at the scale
$Q = M_Z$, the same scale at which all dimensionless MSSM \DRbar
parameters are determined from the Standard Model input parameters.
The inclusion of $\Delta\as^{2L}$ is formally a 4-loop effect on the light
\CP-even Higgs mass in the MSSM\@.  However, $\Delta\as^{2L}$ should
be taken into account for a consistent running and decoupling
procedure with 3-loop renormalization group running.  The red solid
lines in the right panels correspond to the 3-loop calculation of
Ref.~\cite{Harlander:2017kuc}, which uses only the 1-loop threshold correction
$\Delta\as^{1L}$.  These red solid lines are the same as in the
corresponding left panels.  The effect of including
$\Delta\as^{2L}$ is shown as the red dashed line.  We find that the
inclusion of this 2-loop threshold correction leads to an upwards
shift of the Higgs mass by up to $2\unit{GeV}$, depending on \MS and
$X_t$.  Note, that large 4-loop contributions of multiple GeV hint at
a large theoretical uncertainty of the fixed-order calculation of the
light \CP-even Higgs pole mass in parameter regions with multi-TeV
stop masses.

@@

    \code{CKM}, \code{PMNS} &
    CKM and PMNS matrices, respectively, as defined in \cite{Allanach:2008qq}. \\

@@

The \fs user interface for creating spectrum generators for non-SUSY
models is exactly the same as in the case of SUSY models, except that
all non-SUSY parameters are defined in the \MSbar scheme.  In
particular, at the low-energy scale \fs automatically determines
the gauge and Yukawa couplings of the non-SUSY model in the \MSbar
scheme.  For gauge-dependent quantities like running masses and VEVs,
\fs adopts the Feynman gauge, where all gauge fixing parameters
$\xi_i$ are set to unity.

@@

\setlength{\itemindent}{1cm}
